Constraining the Interiors of Asteroids Through Close Encounters

### 2022-04-30 paper/main.tex
Fixed staged

  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for a uniform-density asteroid. The original asteroid shapes were the reference asymmetric (\textit{top}) and symmetric (\textit{bottom}) ellipsoids. In both cases, the density distributions have been extracted assuming a spherical shape. Density is normalized so that mean density is one. The same distance scale is used in all figures. Density distributions show clear pathologies when the incorrect shape is used.}
  \label{fig:sphere-density}
\end{figure*}

@@

  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for non-uniform-density asteroids with mass concentrated in the middle (\textit{top}) and the edges (\textit{bottom}). Density is normalized so that mean density is one. The same distance scale is used in all figures. The extracted distributions agree qualitatively with the true distributions.}
  \label{fig:non-uniform-density}
\end{figure*}

>>>>

  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for a uniform-density asteroid. The original asteroid shapes were the reference asymmetric (\textit{top}) and symmetric (\textit{bottom}) ellipsoids. In both cases, the density distributions have been extracted assuming a spherical shape. Density is normalized so that mean density is one. The same distance scale is used in all figures. Density distributions show clear pathologies when the incorrect shape is used. \jtd{Add uncertainty plots}}
  \label{fig:sphere-density}
\end{figure*}

@@

  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for non-uniform-density asteroids with mass concentrated in the middle (\textit{top}) and the edges (\textit{bottom}). Density is normalized so that mean density is one. The same distance scale is used in all figures. The extracted distributions agree qualitatively with the true distributions. \jtd{Add uncertainty plots}}
  \label{fig:non-uniform-density}
\end{figure*}
